\section{Executive Summary}
I am currently a senior machine learning scientist at TikTok. I obtained my Transportation Ph.D. degree at MIT in 2022 and my dual Master's degree in Transportation and Computer Science at MIT in 2020. Before joining MIT, I obtained my dual Bachelor's degree in Civil Engineering and Management from Tsinghua University. 
% My work utilizes various mathematical techniques including optimization (robust/integer/non-linear), probability and statistics, machine learning (deep/reinforcement learning), econometrics, and game theory. I have published \textbf{{\themyCounter}} peer-reviewed scientific papers (\textbf{{\myFirstAuthor}} first-authored) in leading transportation journals (TR-A, B, C, E, IEEE ITS, TS, etc.). 
% My work at Lyft focuses on real-time driver incentive design. I shipped two iterations of algorithms to over 200 cities and improved 38 million annual profits for the company (validated by A/B test). I designed and delivered the first algorithm-driven free shipping policy from 0 to 1 at TikTok Shop, resulting in 16.7\% increase in ROI. I am currently leading the algorithm development for the Sales \& Operations Planning for TikTok's own warehouse management system from 0 to 1. 
My research focuses on the {resilience of transportation systems with a specific application in public transit (PT), including 1) network performance and passenger behavior monitoring, 2) incident-aware PT control strategy design, and 3) interactions between PT and other transportation modes}. My work utilizes various mathematical techniques including optimization (robust/integer/non-linear), probability and statistics, machine learning (deep/reinforcement learning), econometrics, and game theory. I have published \textbf{{\themyCounterNum}} peer-reviewed scientific papers (\textbf{{\themyFirstAuthorNum}} first-authored) in leading transportation journals (TR-A, B, C, E, IEEE ITS, TS, CACIE, EJOR, Nature Sustainability, etc.). My work resulted in significant industrial impact. During my internship at Lyft, I proposed a new vehicle routing algorithm for bike and scooter rebalancing and battery swap, which saves 1.6 operation million costs per year and has been implemented in all cities with Lyft's micro-mobility services. My work at Lyft focuses on real-time driver incentive design. I shipped two iterations of algorithms to over 200 cities and improved 38 million annual profits for the company (validated by A/B test). At TikTok Shop, I designed and delivered the first algorithm-driven free shipping policy from 0 to 1, resulting in 16.7\% increase in ROI. I am currently leading the supply chain algorithm team at US TikTok Shop, working on problems like optimal fulfillment, inventory placement, demand forecasting, and middle mile optimization.
% My future research interests include multi-modal transportation system resilience as an extension of current work. In a long term, I am interested in exploring blockchain, Web 3.0, cybersecurity and their implementations in data privacy, innovative transportation business, and policy mechanism design. 
% During my master's study, I developed a self-calibrated network performance model for Hong Kong Mass Rail Transit (MTR), which MTR is using for daily service monitoring. I proposed a path recommendation model that can reduce the delay of passengers in the transit system of the Chicago Transit Authority (CTA) by 20\%.