
\section{Work \& Research Experience}
\cventry{Jul 2026 -- Present}{Department of Transportation Engineering, Tsinghua University}{\newline Assistant Professor (Tenure Track)}{}{}{
\begin{itemize}
       \item Principal Investigator of MoS Lab, conducting research and teaching in resilient and intelligent transportation systems, public transit operations, travel demand and behavior modeling, transportation machine learning, and optimization.
\end{itemize}}
\cventry{Dec 2023 -- Jun 2026}{TikTok E-Commerce, Supply Chain and Logistics Team}{\newline Staff Machine Learning Engineer / US Supply Chain Algorithm Lead}{}{}{
\begin{itemize}
       \item Led the US supply chain algorithm team for TikTok Shop, covering algorithms for fulfillment, inventory, warehousing, and middle-mile transportation.
       \item Led the design of the first algorithm-driven free shipping policy for the TikTok E-Commerce platform from 0 to 1 based on \textbf{causal inference models}, increasing the repurchase of the system by 3.2\% while saving 9.2\% total subsidy cost and significantly increasing the shipping subsidy ROI.
       \item Developed the first warehouse-level demand forecasting model for TikTok Shop from 0 to 1 using \textbf{time-series models}, reducing prediction errors from 30\% (manual forecasting) to 10\%. The model replaced the manual procedure for weekly warehouse labor planning.
       \item Received ``M+'' ratings in two consecutive performance reviews, even when the overall E-Commerce organization was rated ``M-''. Awarded 2024 H2 Spot Bonus for exceeding expectation performance (4/100+).
\end{itemize}}
\cventry{Sep 2022 -- Dec 2023}{Lyft Inc., Real Time Supply Management Team}{\newline Senior Research Scientist (T5)}{}{}{
\begin{itemize}
       \item {\textbf{Science tech lead} for Lyft's most important driver incentive product: Real-time Bonus Map. Design the product's future road map for 2024-2025.} 
       \item {Develop a \textbf{heuristic} algorithm to solve a \textbf{nonlinear optimization} model to generate the bonus map for drivers. Commit \textbf{27k+ lines of production codes}. The algorithm is run in real time (every 2 minute) with streaming features.}   
       \item My work improves Lyft's annual rides by 3.3 million and driver hours by 0.93\%, equivalent to \textbf{38 million annual profit} (validated by A/B test). 
       \item Got 2 consecutive ``Exceeding Expectation'' ratings in the performance review, promoted to senior research scientist in a year (the fastest record at Lyft). 
\end{itemize}}

\cventry{May 2022 -- Aug 2022}{Lyft Inc., Transit Bike Scooter (TBS) Operation Technology Team}{\newline Research Scientist Intern}{}{}{
\begin{itemize}
\item {Propose a new initialization algorithm for solving vehicle routing problem in micromobility systems}
\item {Improve the operation efficiency by 4.2\%, equivalent to 1.6 million annual cost saving. Implemented the algorithm to production in all Lyft's micro-mobility service markets}
\item Got intern re-hire offer after the first-half of my intern period because of excellent performance
\end{itemize}}

\cventry{Aug 2018 -- Present}{Urban Mobility Lab and Transit Lab, MIT}{\newline Research Assistant}{}{}{
\begin{itemize}
\item Conducting research in public transit, demand modeling, optimization, and machine learning.
\end{itemize}}

\cventry{Jan, Aug 2020}{Chicago Transit Authority (CTA)}{\newline Research Intern}{}{}{
\begin{itemize}
\item Analyzed the impact of rail disruptions
\item Designed passenger path recommendation strategies under rail disruptions
\end{itemize}}

\cventry{Jul 2019 -- Aug 2019}{Hong Kong Mass Transit Railway (MTR) }{\newline Research Intern}{}{}{
\begin{itemize}
\item Delivered a network performance model which is capable for system performance monitoring. {\href{https://journals.sagepub.com/doi/full/10.1177/0361198120914309}{\textcolor{blue}{\underline{[More]}}}}
\item Gave four training seminars to MTR employees about the model application.
\end{itemize}}


\cventry{Jun -- Jul in 2016 -- 2019}{Singapore-MIT Alliance for Research and Technology (SMART) Center}{\newline Research Intern}{}{}{
\begin{itemize}
\item Analyzed people's preference of autonomous vehicles (AV) {\href{https://www.sciencedirect.com/science/article/abs/pii/S0968090X2100293X}{\textcolor{blue}{\underline{[More]}}}}.
\item Studied the relationship between built environment of travel mode choice.  {\href{https://journals.sagepub.com/doi/full/10.1177/0361198118788423}{\textcolor{blue}{\underline{[More]}}}}
\item Simulated the interaction between AV and public transit from a competitive perspective. {\href{https://www.sciencedirect.com/science/article/abs/pii/S0968090X21000863}{\textcolor{blue}{\underline{[More]}}}}
\end{itemize}}

\cventry{Dec 2015 --Aug 2018}{Institute of Transportation Research, Tsinghua University}{\newline Research Assistant}{}{}{
\begin{itemize}
\item Proposed a vehicle speed profile estimation model. {\href{https://www.sciencedirect.com/science/article/pii/S0968090X17301870}{\textcolor{blue}{\underline{[More]}}}}
\item Analyzed people's satisfaction of on-street parking. {\href{https://doi.org/10.1016/j.tra.2021.04.013}{\textcolor{blue}{\underline{[More]}}}} 
\end{itemize}} 
